Democracy, Public Support, and Measurement Uncertainty

### 2021-07-09 paper/dcpo_demsupport.Rmd
add sentences on MOC and overimputation

## Incorporating Uncertainty
Although measurement uncertainty has yet not attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
Especially when measurement error is correlated with the dependent variable, the resulting bias could either attentuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, 360].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey_policy_2018, 254].

Therefore, after we replicate the original analyses that used only the point estimates of democratic support, we incorporate the full distribution of the latent variable estimates.
To do this, we replicate the latent variable estimation from the original survey data, duplicate each article's analysis dataset 1,000 times, and assign to each a different random draw from the posterior distribution of public democratic support.
Then we perform each analysis repeatedly on its respective collection of datasets, and combine the results following the rules set out in @Rubin1987 [see, e.g., @Schnakenberg2014; @Crabtree2015].
Our approach of incorporating uncertainty is similar in the logic of @Blackwell2017a's multiple overimputation, that is, creating multiple data set from the posterior distribution of the true latent value, applying analysis model for each dataset, and then averaging results by using Rubin's rule.

>>>>

## Incorporating Uncertainty
Although measurement uncertainty has yet not attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
Especially when measurement error is correlated with the dependent variable, the resulting bias could either attentuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, 360; @caughey_policy_2018, 254].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey_policy_2018, 254].

Therefore, after we replicate the original analyses that used only the point estimates of democratic support, we incorporate the full distribution of the latent variable estimates.
To do this, we replicate the latent variable estimation from the original survey data, duplicate each article's analysis dataset 1,000 times, and assign to each a different random draw from the posterior distribution of public democratic support.
Then we perform each analysis repeatedly on its respective collection of datasets, and combine the results following the rules set out in @Rubin1987 [see, e.g., @Schnakenberg2014; @Crabtree2015].
Our approach of incorporating uncertainty is analogous to @Blackwell2017a's multiple overimputation which corrects the Between imputation variance. 
We also employ one alternative technique known as “method of composition” [@treier_democracy_2008, 215) as robuestness check [see Supplementary Appendix xx].
